All Your Graphs Belong to Us

### 2012-07-18 doc/asplos13/evaluation.tex
comment out UTS code snippet in eval
added paragraph making note of Cray XMT UTS results

We ran UTS-mem on Grappa and the XMT with two different 100M-vertex trees with a geometric distribution numChildren distribution. Figure~\ref{fig:grappa-xmt-uts} shows the performance in terms of number of vertices visited per second versus number of compute nodes. The Grappa results are for the best parameter values from a limited search over \flushtimeout~and \asyncforthr~\TODO{want to say this in general at beginning of eval?}. Grappa achieves 3x better performance for 12 nodes. Scaling up, Grappa adds 2Mvert/s/node versus XMT's 850Kvert/s/node.
\TODO{why is XMT getting different results for T1L,T2L; would expect it to be the machine with the most uniform results.}

>>>>

We ran UTS-mem on Grappa and the XMT with two different 100M-vertex trees with a geometric distribution numChildren distribution. Figure~\ref{fig:grappa-xmt-uts} shows the performance in terms of number of vertices visited per second versus number of compute nodes. The Grappa results are for the best parameter values from a limited search over \flushtimeout~and \asyncforthr~\TODO{want to say this in general at beginning of eval?}. Grappa achieves 3x better performance for 12 nodes. Scaling up, Grappa adds 2Mvert/s/node versus XMT's 850Kvert/s/node.

\TODO{why is XMT getting different results for T1L,T2L; would expect it to be the machine with the most uniform results.}

{\em you can rewrite this or blow it off -- just trying to get some thoughts in before leaving}
Despite our efforts to tune the UTS implementation specific to Cray XMT, performance does not scale well with increasing processor count, flattening out around sixty processors.  When we increase the size of the tree, we find that performance does not improve, suggesting that performance is not limited by task parallelism.   Cray's performance tools show that an increasing number of memory retry operations are generated by code within the runtime system.  Retries are performed by the memory controller when remote synchronization operations fail to find the full-bit associated with each memory location in the unavailable state.  Retries are issued at low priority relative to new memory operations issued by the processor by other contexts, so they consume what would otherwise be unused injection bandwidth.  On a full-bandwidth system such as the MTA-2, retries have no impact on the progress of tasks other than their own.  On a Cray XMT, network bandwidth is limited, so retries create congestion.  In comparison, Grappa performs synchronization without retries, delaying response at the receiving end until ready to notify the sender to proceed.  This saves bandwidth and permits scaling of tasks performing synchronization even on low injection rate networks.
